Current and future constraints on primordial magnetic fields

### 2017-01-30 pmf.tex

>>>>

Between each stage of ground-based CMB experiment, the number of detectors increases by an order of magnitude. Adding detectors will always reduce the noise in the instrument, making it easier to isolate the PMF signal, thereby reducing the uncertainty on PMF measurements. When quantifying the effects of the number of detectors it is more informative to use polarisation noise, as detector count relies on knowing the individual sensitivity of each detector. As such, we give our result in terms of polarisation noise, noting that polarisation noise scales with detector count as $\sqrt{N_{detectors}}$

We find that
